fGFPCA dynamic prediction

### 2023-02-21 f-GFPCA.Rmd
make figure for proposal report:

  out_pred_lap_subj1 %>% 
    group_by("type") %>%
    ggplot()+
    geom_line(aes(x=mid, y=true), col = "black")+
    geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
              show.legend = FALSE)+
    labs(x="Binned time", title = "Subject 1 out-of-sample Laplace"),

@@

  out_pred_lap_subj2 %>% 
    group_by("type") %>%
    ggplot()+
    geom_line(aes(x=mid, y=true), col = "black")+
    geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
              show.legend = FALSE)+
    labs(x="Binned time", title = "Subject 2 out-of-sample Laplace"),

@@

  out_pred_lap_subj3 %>% 
    group_by("type") %>%
    ggplot()+
    geom_line(aes(x=mid, y=true), col = "black")+
    geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
              show.legend = FALSE)+
    labs(x="Binned time", title = "Subject 2 out-of-sample Laplace"),

@@

  out_pred_lap_subj4 %>% 
    group_by("type") %>%
    ggplot()+
    geom_line(aes(x=mid, y=true), col = "black")+
    geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
              show.legend = FALSE)+
    labs(x="Binned time", title = "Subject 2 out-of-sample Laplace"),

>>>>

  # out_pred_lap_subj1 %>% 
  #   group_by("type") %>%
  #   ggplot()+
  #   geom_line(aes(x=mid, y=true), col = "black")+
  #   geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
  #             show.legend = FALSE)+
  #   labs(x="Binned time", title = "Subject 1 out-of-sample Laplace"),

@@

  # out_pred_lap_subj2 %>% 
  #   group_by("type") %>%
  #   ggplot()+
  #   geom_line(aes(x=mid, y=true), col = "black")+
  #   geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
  #             show.legend = FALSE)+
  #   labs(x="Binned time", title = "Subject 2 out-of-sample Laplace"),

@@

  # out_pred_lap_subj3 %>% 
    # group_by("type") %>%
    # ggplot()+
    # geom_line(aes(x=mid, y=true), col = "black")+
    # geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
    #           show.legend = FALSE)+
    # labs(x="Binned time", title = "Subject 2 out-of-sample Laplace"),

@@

  # out_pred_lap_subj4 %>% 
  #   group_by("type") %>%
  #   ggplot()+
  #   geom_line(aes(x=mid, y=true), col = "black")+
  #   geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
  #             show.legend = FALSE)+
  #   labs(x="Binned time", title = "Subject 2 out-of-sample Laplace"),
  #
